Investigation of Limited Detection Schemes for Light Scattering of Optically Trapped Asymmetric Particles

### 2022-11-22 Manuscript_rev1.tex
Add files via upload

Using our simulation from Section~\ref{sec:brownian} we calculated the instantaneous signal from our dimer at each time step using MSTM.  We applied Eq.~\eqref{eq:bayes} --- covered in Section~\ref{sec:Bayes} --- and the reference orientation with the highest probability is taken as our estimation of the dimer's instantaneous orientation. To visualise our model's performance  we plotted the radial distance between our estimation $\hat{\bf n}_{est}$ of the orientation and the dimer's \emph{actual} instantaneous orientation $\hat{\bf s}$ versus time. For comparison, we also plotted the radial distance between the closest reference orientation, denoted $\hat{\bf n}_{best}$, and the dimer's instantaneous orientation. If we assume our prior of the reference orientations $p(\hat{\bf n}_\alpha)$ to be uniform the performance is rather poor, as seen in \ref{fig:uniform}.

@@

The reasoning for this lies with the fact that differences in reference signals and reference orientation spacing are not directly correlated with each other. To remedy this we need to account for the fact that a trapped dimer's motion is severely limited due to the trap stiffness. Therefore, the prior of the reference orientations $p(\hat{\bf n}_\alpha)$ was defined at each time step by accounting for the physical distance between our previous estimate $\hat{\bf n}_{\alpha}(t - \Delta t)$ and each reference orientation $\hat{\bf n}_\alpha(t)$:

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results and  Discussion}
\label{sec:Discussion}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Asymmetric dimer dynamics}
\label{sec:motion}

@@

\newpage
\appendix
\onecolumn
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Appendix}
\setcounter{table}{0}
\renewcommand{\thetable}{A\arabic{table}}
\label{sec:App1}
\begin{table}[h]
\begin{center}
\caption{\label{tab:A1}
%
Reference Orientations vector components$^*$}
\begin{tabular}{|c|c|c|c|}
\hline\hline
Reference Orientation & $\hat{\bf n}_{i,\ x}$ &  $\hat{\bf n}_{i,\ y}$ &  $\hat{\bf n}_{i,\ z}$ \\
\hline
$1$ & $ 0.29588$ &  $ 0.29588$ & $ 0.90825$ \\
$2$ & $ 0.90825$ &  $ 0.29588$ & $ 0.29588$ \\
$3$ & $ 0.29588$ &  $ 0.90825$ & $ 0.29588$ \\
$4$ & $1.0000$ &  $0.00000$ & $0.00000$ \\
$5$ & $0.00000$ &  $1.0000$ & $0.00000$ \\
$6$ & $0.00000$ &  $0.00000$ & $1.0000$ \\
$7$ & $ 0.29588$ &  $ 0.29588$ & $-0.90825$ \\
$8$ & $ 0.90825$ &  $ 0.29588$ & $-0.29588$ \\
$9$ & $ 0.29588$ &  $ 0.90825$ & $-0.29588$ \\
$10$ & $0.00000$ &  $0.00000$ & $-1.0000$ \\
$11$ & $ 0.29588$ &  $-0.29588$ & $ 0.90825$ \\
$12$ & $ 0.90825$ &  $-0.29588$ & $ 0.29588$ \\
$13$ & $ 0.29588$ &  $-0.90825$ & $ 0.29588$ \\
$14$ & $0.00000$ &  $-1.0000$ & $0.00000$ \\
$15$ & $ 0.29588$ &  $-0.29588$ & $-0.90825$ \\
$16$ & $ 0.90825$ &  $-0.29588$ & $-0.29588$ \\
$17$ & $ 0.29588$ &  $-0.90825$ & $-0.29588$ \\
$18$ & $-0.29588$ &  $ 0.29588$ & $ 0.90825$ \\
$19$ & $-0.90825$ &  $ 0.29588$ & $ 0.29588$ \\
$20$ & $-0.29588$ &  $ 0.90825$ & $ 0.29588$ \\
$21$ & $-1.0000$ &  $0.00000$ & $0.00000$ \\
$22$ & $-0.29588$ &  $ 0.29588$ & $-0.90825$ \\
$23$ & $-0.90825$ &  $ 0.29588$ & $-0.29588$ \\
$24$ & $-0.29588$ &  $ 0.90825$ & $-0.29588$ \\
$25$ & $-0.29588$ &  $-0.29588$ & $ 0.90825$ \\
$26$ & $-0.90825$ &  $-0.29588$ & $ 0.29588$ \\
$27$ & $-0.29588$ &  $-0.90825$ & $ 0.29588$ \\
$28$ & $-0.29588$ &  $-0.29588$ & $-0.90825$ \\
$28$ & $-0.90825$ &  $-0.29588$ & $-0.29588$ \\
$30$ & $-0.29588$ &  $-0.90825$ & $-0.29588$ \\
\hline\hline
\multicolumn{4}{l}{\small *Orientation vector points from centre of sphere 1 to centre of sphere 2.} \\
		\end{tabular}
	\end{center}
\end{table}

\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[h]
  \begin{center}
    \caption{\label{tab:A2}
      % 
      Raw intensities $I_k^*$ and scaled intensities $y_k$}
    \begin{tabular}{|c|c|c|c|c|c|c|}
      \hline\hline
      Reference Orientation  & $I(\hat{\bf n}_i,\ 15^{\circ})$ &  $I(\hat{\bf n}_i, \ 45^{\circ})$ &  $I(\hat{\bf n}_i,\ 90^{\circ})$ & $y(\hat{\bf n}_i, \ 15^{\circ})$ & $y(\hat{\bf n}_i, \ 45^{\circ})$ & $y(\hat{\bf n}_i, \ 90^{\circ})$ \\
\hline
$1$ & $13.371$ & $0.1264$ & $0.0122$ & $-0.5423$ & $-0.4253$ & $-0.4838$ \\
$2$ & $13.237$ & $0.0272$ & $0.0102$ & $0.2429$ & $-1.401$ & $-0.7826$ \\
$3$ & $15.840$ & $0.1072$ & $0.0234$ & $1.337$ &$-0.6142$&	$1.162$ \\
$4$ & $12.657$ & $0.2246$ & $0.0244$ & $-0.0012$ &	$0.5399$ & $0.9695$ \\
$5$ & $15.351$ & $0.0527$ & $0.0221$ & $1.132$ &	$-1.150$ & $1.303$ \\
$6$ & $12.046$ & $0.0916$ & $0.0142$ & $-0.2584$ &	$-0.7676$ &	$-0.1886$ \\
$7$ & $11.376$ & $0.0036$ & $0.0095$ & $-0.5403$ &$-1.633$ & $-0.8792$ \\
$8$ & $13.130$ & $0.2346$ & $0.0095$ & $0.1977$ & $0.6379$ & $-0.8794$ \\
$9$ & $15.975$ & $0.2893$ & $0.0273$ & $1.38724$ & $1.175$ & $1.726$ \\
$10$ & $10.073$ & $0.2933$ & $0.0221$ & $-1.088$	& $1.215$ & $0.9641$ \\
$11$ & $11.371$ & $0.1264$ & $0.0122$ & $-0.5423$ & $-0.4253$ & $-0.4838$ \\
$12$ & $13.238$ & $0.0272$ & $0.0102$ & $0.2429$ &	$-1.401$ & $-0.7826$ \\
$13$ & $15.840$ & $0.1072$ & $0.0234$ & $1.337$ &	$-0.6142$ & $1.162$ \\
$14$ & $15.351$ & $0.0527$ & $0.0244$ & $1.132$ & $-1.150$ & $1.303$ \\
$15$ & $13.376$ & $0.0036$ & $0.0095$ & $-0.5403$ & $-1.633$ & $-0.8792$ \\
$16$ & $13.130$ & $0.2346$ & $0.0095$ & $0.1977$ & $0.6379$ & $-0.8794$ \\
$17$ & $15.957$ & $0.2893$ & $0.0273$ & $1.387$	& $1.175$	& $1.726$ \\
$18$ & $14.199$ & $0.0935$ & $0.0076$ & $0.6472$ & $-0.7496$ & $-1.158$ \\
$19$ & $8.5164$ & $0.3133$ & $0.0076$ & $-1.743$ & $1.411$ & $-1.157$ \\
$20$ & $12.961$ & $0.2420$ & $0.0188$ & $0.1267$ & $0.7113$ & $0.4765$ \\
$21$ & $8.2160$ & $0.3217$ & $0.0142$ & $-1.869$ & $1.495$ & $-0.1890$ \\
$22$ & $14.212$ & $0.2537$ & $0.0102$ & $0.6529$ & $0.8265$ & $-0.7835$ \\
$23$ & $8.9280$ & $0.1398$ & $0.0123$ & $-1.570$ &	$-0.2934$ & $-0.4840$ \\
$24$ & $13.328$ & $0.1964$ & $0.0234$ & $0.2807$ & $0.2624$ & $1.162$ \\
$25$ & $14.199$ & $0.0935$ & $0.0076$ & $0.6472$ & $-0.7496$ & $-1.1580$ \\
$26$ & $8.5164$ & $0.3133$ & $0.0076$ & $-1.743$	& $1.411$ & $-1.157$ \\
$27$ & $12.961$ & $0.2420$ & $0.0188$ & $0.1267$	& $0.7113$ & $0.4765$ \\
$28$ & $14.212$ & $0.2537$ & $0.0102$ & $0.6529$ & $0.8265$ & $-0.7835$ \\
$29$ & $8.9280$ & $0.1398$ & $0.0122$ & $-1.570$ &	$-0.2934$ & $-0.4840$ \\
$30$ & $13.328$ & $0.1964$ & $0.0234$ & $0.2807$ & $0.2624$ & $1.162$ \\
\hline\hline
\multicolumn{7}{l}{\small *$I_k$ values are calculated using MSTM package.}
\end{tabular}
\end{center}
\end{table}

>>>>

Using our simulation from Section~\ref{sec:brownian} we calculated the instantaneous signal from our dimer at each time step using MSTM.  We applied Eq.~\eqref{eq:bayes} --- covered in Section~\ref{sec:Bayes} --- and the reference orientation with the highest probability is taken as our estimation of the dimer's instantaneous orientation. To visualise our model's performance  we plotted the radial distance between our estimation $\hat{\bf n}_{est}$ of the orientation and the dimer's \emph{actual} instantaneous orientation $\hat{\bf s}$ versus time. For comparison, we also plotted the radial distance between the closest reference orientation, denoted $\hat{\bf n}_{best}$, and the dimer's instantaneous orientation. If we assume our prior of the reference orientations $p(\hat{\bf n}_\alpha)$ to be uniform the performance is poor, as seen in \ref{fig:uniform}.

@@

The reasoning for this lies with the fact that differences in reference signals and reference orientation spacing are not directly correlated with each other. In some cases, two reference orientation will have identical signal responses. To remedy this we need to account for the fact that a trapped dimer's motion is severely limited due to the trap stiffness. Therefore, the prior of the reference orientations $p(\hat{\bf n}_\alpha)$ was defined at each time step by accounting for the physical distance between our previous estimate $\hat{\bf n}_{\alpha}(t - \Delta t)$ and each reference orientation $\hat{\bf n}_\alpha(t)$:

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results and  Discussion}
\label{sec:Discussion}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Asymmetric dimer dynamics}
\label{sec:motion}

@@

\newpage
\appendix
\onecolumn
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Appendix}
\setcounter{table}{0}
\renewcommand{\thetable}{A\arabic{table}}
\label{sec:App1}
\begin{table}[h]
\begin{center}
\caption{\label{tab:A1}
%
Reference Orientations vector components$^*$}
\begin{tabular}{|c|c|c|c|}
\hline\hline
Reference Orientation & $\hat{\bf n}_{\alpha,\ x}$ &  $\hat{\bf n}_{\alpha,\ y}$ &  $\hat{\bf n}_{\alpha,\ z}$ \\
\hline
$1$  & $ 0.29588$ &  $ 0.29588$ & $ 0.90825$ \\
$2$  & $ 0.90825$ &  $ 0.29588$ & $ 0.29588$ \\
$3$  & $ 0.29588$ &  $ 0.90825$ & $ 0.29588$ \\
$4$  & $ 1.00000$ &  $ 0.00000$ & $ 0.00000$ \\
$5$  & $ 0.00000$ &  $ 1.00000$ & $ 0.00000$ \\
$6$  & $ 0.00000$ &  $ 0.00000$ & $ 1.00000$ \\
$7$  & $ 0.29588$ &  $ 0.29588$ & $-0.90825$ \\
$8$  & $ 0.90825$ &  $ 0.29588$ & $-0.29588$ \\
$9$  & $ 0.29588$ &  $ 0.90825$ & $-0.29588$ \\
$10$ & $ 0.00000$ &  $ 0.00000$ & $-1.00000$ \\
$11$ & $ 0.29588$ &  $-0.29588$ & $ 0.90825$ \\
$12$ & $ 0.90825$ &  $-0.29588$ & $ 0.29588$ \\
$13$ & $ 0.29588$ &  $-0.90825$ & $ 0.29588$ \\
$14$ & $ 0.00000$ &  $ -1.0000$ & $ 0.00000$ \\
$15$ & $ 0.29588$ &  $-0.29588$ & $-0.90825$ \\
$16$ & $ 0.90825$ &  $-0.29588$ & $-0.29588$ \\
$17$ & $ 0.29588$ &  $-0.90825$ & $-0.29588$ \\
$18$ & $-0.29588$ &  $ 0.29588$ & $ 0.90825$ \\
$19$ & $-0.90825$ &  $ 0.29588$ & $ 0.29588$ \\
$20$ & $-0.29588$ &  $ 0.90825$ & $ 0.29588$ \\
$21$ & $-1.00000$ &  $ 0.00000$ & $ 0.00000$ \\
$22$ & $-0.29588$ &  $ 0.29588$ & $-0.90825$ \\
$23$ & $-0.90825$ &  $ 0.29588$ & $-0.29588$ \\
$24$ & $-0.29588$ &  $ 0.90825$ & $-0.29588$ \\
$25$ & $-0.29588$ &  $-0.29588$ & $ 0.90825$ \\
$26$ & $-0.90825$ &  $-0.29588$ & $ 0.29588$ \\
$27$ & $-0.29588$ &  $-0.90825$ & $ 0.29588$ \\
$28$ & $-0.29588$ &  $-0.29588$ & $-0.90825$ \\
$28$ & $-0.90825$ &  $-0.29588$ & $-0.29588$ \\
$30$ & $-0.29588$ &  $-0.90825$ & $-0.29588$ \\
\hline\hline
\multicolumn{4}{l}{\small *Orientation vector points from centre of sphere 1 to centre of sphere 2.} \\
		\end{tabular}
	\end{center}
\end{table}

\newpage
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[h]
  \begin{center}
    \caption{\label{tab:A2}
      % 
      Raw intensities $I_k^*$ and scaled intensities $y_k$}
    \begin{tabular}{|c|c|c|c|c|c|c|}
      \hline\hline
      Reference Orientation  & $I(\hat{\bf n}_\alpha\ ,\ 15^{\circ})$ &  $I(\hat{\bf n}_\alpha \ , \ 45^{\circ})$ &  $I(\hat{\bf n}_\alpha \ ,\ 90^{\circ})$ & $y(\hat{\bf n}_\alpha \ , \ 15^{\circ})$ & $y(\hat{\bf n}_\alpha \ , \ 45^{\circ})$ & $y(\hat{\bf n}_\alpha \ , \ 90^{\circ})$ \\
\hline
$1$  & $13.371$ & $0.1264$ & $0.0122$ & $-0.5423$ & $-0.4253$ & $-0.4838$ \\
$2$  & $13.237$ & $0.0272$ & $0.0102$ & $ 0.2429$ & $-1.4010$ & $-0.7826$ \\
$3$  & $15.840$ & $0.1072$ & $0.0234$ & $ 1.3370$ & $-0.6142$ & $ 1.1620$ \\
$4$  & $12.657$ & $0.2246$ & $0.0244$ & $-0.0012$ &	$ 0.5399$ & $ 0.9695$ \\
$5$  & $15.351$ & $0.0527$ & $0.0221$ & $ 1.1320$ & $-1.1500$ & $ 1.3030$ \\
$6$  & $12.046$ & $0.0916$ & $0.0142$ & $-0.2584$ &	$-0.7676$ &	$-0.1886$ \\
$7$  & $11.376$ & $0.0036$ & $0.0095$ & $-0.5403$ & $-1.6330$ & $-0.8792$ \\
$8$  & $13.130$ & $0.2346$ & $0.0095$ & $ 0.1977$ & $ 0.6379$ & $-0.8794$ \\
$9$  & $15.975$ & $0.2893$ & $0.0273$ & $ 1.3872$ & $ 1.1750$ & $ 1.7260$ \\
$10$ & $10.073$ & $0.2933$ & $0.0221$ & $-1.0880$ & $ 1.2150$ & $ 0.9641$ \\
$11$ & $11.371$ & $0.1264$ & $0.0122$ & $-0.5423$ & $-0.4253$ & $-0.4838$ \\
$12$ & $13.238$ & $0.0272$ & $0.0102$ & $ 0.2429$ &	$-1.4010$ & $-0.7826$ \\
$13$ & $15.840$ & $0.1072$ & $0.0234$ & $ 1.3370$ & $-0.6142$ & $ 1.1620$ \\
$14$ & $15.351$ & $0.0527$ & $0.0244$ & $ 1.1320$ & $-1.1500$ & $ 1.3030$ \\
$15$ & $13.376$ & $0.0036$ & $0.0095$ & $-0.5403$ & $-1.6330$ & $-0.8792$ \\
$16$ & $13.130$ & $0.2346$ & $0.0095$ & $ 0.1977$ & $ 0.6379$ & $-0.8794$ \\
$17$ & $15.957$ & $0.2893$ & $0.0273$ & $ 1.3870$ & $ 1.1750$ & $ 1.7260$ \\
$18$ & $14.199$ & $0.0935$ & $0.0076$ & $ 0.6472$ & $-0.7496$ & $-1.1580$ \\
$19$ & $8.5164$ & $0.3133$ & $0.0076$ & $-1.7430$ & $ 1.4110$ & $-1.1570$ \\
$20$ & $12.961$ & $0.2420$ & $0.0188$ & $ 0.1267$ & $ 0.7113$ & $ 0.4765$ \\
$21$ & $8.2160$ & $0.3217$ & $0.0142$ & $-1.8690$ & $ 1.4950$ & $-0.1890$ \\
$22$ & $14.212$ & $0.2537$ & $0.0102$ & $ 0.6529$ & $ 0.8265$ & $-0.7835$ \\
$23$ & $8.9280$ & $0.1398$ & $0.0123$ & $-1.5700$ &	$-0.2934$ & $-0.4840$ \\
$24$ & $13.328$ & $0.1964$ & $0.0234$ & $ 0.2807$ & $ 0.2624$ & $ 1.1620$ \\
$25$ & $14.199$ & $0.0935$ & $0.0076$ & $ 0.6472$ & $-0.7496$ & $-1.1580$ \\
$26$ & $8.5164$ & $0.3133$ & $0.0076$ & $-1.7430$ & $ 1.4110$ & $-1.1570$ \\
$27$ & $12.961$ & $0.2420$ & $0.0188$ & $ 0.1267$ & $ 0.7113$ & $ 0.4765$ \\
$28$ & $14.212$ & $0.2537$ & $0.0102$ & $ 0.6529$ & $ 0.8265$ & $-0.7835$ \\
$29$ & $8.9280$ & $0.1398$ & $0.0122$ & $-1.5700$ & $-0.2934$ & $-0.4840$ \\
$30$ & $13.328$ & $0.1964$ & $0.0234$ & $ 0.2807$ & $ 0.2624$ & $ 1.1620$ \\
\hline\hline
\multicolumn{7}{l}{\small *$I_k$ values are calculated using MSTM package.}
\end{tabular}
\end{center}
\end{table}
